### 2017-02-07 presentation/slides.tex
Fix typos in presentation

\begin{frame}{What is \epto{}?}
	\textbf{Epidemic Total Order Algorithm:}
	\begin{itemize}
		\item Probabilistic dissemination algorithm
			\begin{itemize}
				\item Using balls-and-bins
			\end{itemize}
		\item Provides deterministic total order
		\item Scales wells with the number of peers
			\begin{itemize}
				\item Parameters increase logarithmically
			\end{itemize}
		\item Churn resistant
	\end{itemize}
\end{frame}

@@

\begin{frame}{Evaluation}
    We evaluate \epto{} against \jgroups{}, scaling peers and global event throughput per second.

>>>>

\begin{frame}{What is \epto{}?}
	\textbf{Epidemic Total Order Algorithm:}
	\begin{itemize}
		\item Probabilistic dissemination algorithm
			\begin{itemize}
				\item Using balls-and-bins
			\end{itemize}
		\item Provides deterministic total order,  integrity and validity
		\item Scales well with the number of peers
			\begin{itemize}
				\item Parameters increase logarithmically
			\end{itemize}
		\item Churn resistant
	\end{itemize}
\end{frame}

@@

\begin{frame}{Evaluation}
    We evaluate \epto{} against \jgroups{} SEQUENCER, scaling peers and global event throughput per second.
